---
title: "P8105_hw4_mc4433"
author: "Manqi Cai"
date: "10/25/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, include=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(haven)
library(ggridges)
library(ggthemes)
library(janitor)
```

#Problem 1 
The project lead will load and tidy the data for this problem. The original data file includes data in “wide” format: the post-natal days on which developmental landmarks are reached are stored in columns called PD_outcome. The project lead will convert these data to “long” format, using reasonable variable names and values.

The collaborator will create a plot showing the distribution of post-natal days for each developmental landmark.

#Problem 2 
The project lead will load and tidy the data for this problem. Combine the data in pols-month.csv and GDP.csv based on the date / month (use lubridate::floor_date to collase dates to the first day of the month).

The collaborator will create a plot showing the GDP value over time, including the party of the president in an informative aesthetic.

```{r load datasets}
pols_month_data <- read_csv("../data/fivethirtyeight_datasets/pols-month.csv", col_types = "ciiiiiiii") %>%
  clean_names() %>%
  mutate(mon = as.Date(mon),
         mon = lubridate::floor_date(mon, unit = "month")) %>% 
  rename(date = mon)
   

gdp_data <- read_csv("../data/fivethirtyeight_datasets/GDP.csv") %>%
  clean_names() %>% 
  mutate(date = lubridate::floor_date(date, unit = "month"))

```

```{r load and tidy data}
combine_data <- inner_join(pols_month_data, gdp_data, by = "date") %>% 
  mutate(president = ifelse(prez_dem == 1, "dem", "gop")) %>% 
  select(- prez_gop, - prez_dem)
```